An Embedding Framework for Consistent Polyhedral Surrogates

### 2019-05-22 neurips-19/poly-embed.tex
partly through sec 4

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.
In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
We illustrate our construction in the following section.

\raf{Bo: this proves one of your lemmas}
\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there is a ``valid'' \raf{my scare quotes} link from $\Gamma$ to $\gamma$. % which can be taken to be separated if $L$ is polyhedral.
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
\end{proof}

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}

>>>>

We have now seen the tight relationship between polyhedral losses and embeddings; in particular, every polyhedral loss embeds some discrete loss.
The embedding itself tells us how to map the embedded points back to the discrete reports (map $\varphi(r)$ to $r$), but it is not clear when this map can be extended to the remaining reports to obtain a full link function, and whether such a link can lead to consistency.

In this section, we give a construction to generate calibrated links for \emph{any} polyhedral loss.
The first step is to give a link $\psi$ such that minimizing expected surrogate loss, followed by applying $\psi$, minimizes expected original loss.

\begin{proposition}\label{prop:embed-link}
  Let $L$ elicit $\Gamma:\simplex\toto\reals^d$ which embeds a finite property $\gamma$.
  Then there exists a link function $\psi: \reals^d \to \R$ that is \emph{valid} in the sense that, for any $p$, if $u$ minimizes expected $L$-loss (i.e. $u \in \Gamma(p)$, then $\psi(u)$ minimizes expected $\ell$-loss (i.e. $\psi(u) \in \gamma(p)$).
\end{proposition}
\begin{proof}
  Let $\gamma:\simplex\toto\R$.
  Proposition~\ref{prop:embed-trim} gives us that $\trim(\Gamma) = \{\gamma_r : r\in\R\}$.
  Then for any $u\in\reals^d$, there is some $r\in\R$ such that $\Gamma_u \subseteq \gamma_r$.
  The link $\psi : \reals^d \to \R$ which encodes these choices is valid.
\end{proof}

However, this guarantee is weak: for a given $p$, $u$ could be arbitrarily close to optimal with respect to $L$, yet $\psi(u)$ could remain arbitrarily wrong.
This kind of problem is ruled out by constructing a $\psi$ that is furthermore \emph{calibrated} (Definition \ref{def:calibrated}).
The main construction begins from the intuitive approach of ``thickening'' the embedding points, by causing all $u$ in the neighborhood of an embedding point to link back to the corresponding report.
However, we must consider cases where $\Gamma(p)$, the set of optimal $u$, is larger than just one embedding point.
These cases have a nice structure:

\begin{lemma}
  \label{lem:polyhedral-range-gamma}
  Let $L:\reals^d\to\reals_+^\Y$ be a polyhedral loss, and let $\Gamma = \prop{L}$.
  Then the range of $\Gamma$, $\U = \Gamma(\simplex) = \{\Gamma(p) \subseteq \reals^d | p\in\simplex\}$, is a finite set of closed polyhedra.
\end{lemma}
For each of these finitely many $U \in \U$, we let $R_U$ be the set of reports whose embedding points lie in $U$.
The idea will be to map points in $U$, as well as nearby  to something in $R_U$
%We show in the full version \bo{okay wording?} that for any $p$, if $U = \Gamma(p)$, then $R_U = \gamma(p)$.

\begin{definition} \label{def:eps-thick-link}
  Given a polyhedral $L$ embedding some $\ell$, an $\epsilon > 0$, and a norm $\|\cdot\|$, the \emph{$\epsilon$-thickened link} $\psi$ is constructed as follows.
  First, initialize $\Psi: \reals^d \toto \R$ by setting $\Psi(u) = \R$ for all $u$.
  Then for each $U \in \U$, for all points $u$ such that $\inf_{u^* \in U} \|u^*-u\| < \epsilon$, update $\Psi(u) = \Psi(u) \cap R_U$.
  Finally, define $\psi(u) \in \Psi(u)$, breaking ties arbitrarily.
  If $\Psi(u)$ became empty, then leave $\psi(u)$ undefined.
\end{definition}
